\section{Architecture}

\subsection*{Overview of Technologies}

At the start we did not have any preference of technologies to chose and how to go about the architecture. In the first sprint this is what we had planned.
Member in the team were familiar with Java, Gradle, maven and wanted to try out Kotlin because it is a language that is more modern and popular to learn than Java.
Some member also had previous experience in developing a simple REST application and this can be designed to our requirements we choice this architecture at the start. This is the choices of technologies we did and a little few toughts on architecture design.

The backend is developed with Spring as it has web services, web security,
and data persistence, making it a suitable choice for developing a REST API.
For unit testing Junit is used as we are familiar with it and it is widely used in gradle applications.

Docker is used to ensure that the backend application runs in a consistent and isolated environment,
independent of the underlying infrastructure.
This reduces issues related to environment differences between development and deployment,
and simplifies setup for team members. 

For the frontend, we use React with TypeScript.
React was selected because it is widely used in web application development.
TypeScript was chosen over Javascript as it helps improve code quality and maintainability through stronger type checking.
React Router was used in addition to structure the application into pages and make navigation and architecture easier to manage.

% this could be a diagram or picture
The technologies used in the project is as follows:
\begin{itemize}
    \item Kotlin for the programming language
    \item Spring Framework for backend development
    \item PostgreSQL for databases
    \item Docker for container management and orchestration
    \item React and TypeScript for frontend development
\end{itemize}

%At the current stage, the frontend and backend are still being developed partly independently.
%As a result, some integration remains incomplete, and in certain cases mocking or partial functionality
%has been necessary during development.


\subsection{How Much Up-Front?} %TODO endre tittel?  
Based on our experience in the project, we performed relatively little upfront architectural work.
This was mainly due to time constraints, learning new technologies, and a focus on delivering working functionality early in the development process.
This aligns with agile principles, where teams often aim to design “just enough” architecture to get started.

However, when reflecting on the paper\cite{UpFront}, our approach may have been leaning too far towards minimal upfront design.
The paper highlights that too little upfront planning can lead to an “accidental architecture”,
where decisions are made reactively rather than strategically.
Although we have not yet encountered major issues caused by this,
it introduces a risk of architectural inconsistencies as the system grows.
there are clear areas where this could become problematic, particularly as new
features are introduced.

For example, decisions regarding authentication and integration with external systems,
such as institutional login solutions, have not been planned in advance.
Introducing such functionality at a later stage may require significant restructuring
of both frontend and backend components, highlighting a potential architectural gap.

At the same time, our project included some factors such as needing to deliver functionality early, which supports a more emergent architecture approach.
According to the paper, this justifies reducing upfront work in order to remain flexible and responsive to change. 

In hindsight, a slightly higher level of upfront architectural planning would likely have been beneficial,
especially in identifying external requirements and defining key system boundaries earlier.
This could have reduced the risk of future refactoring while still maintaining flexibility.

Overall, our architectural decisions were discussed, but not always systematically planned.
The project reflects the trade-off described in the paper.
Although our current approach has worked so far, a more balanced approach between upfront planning and emergent design would likely improve the system as it expands.


\subsection{Architectural Concerns}
In our project we do not have a formally assigned software architect.
Instead, architectural responsibility is shared across the team,
with each member expected to consider how their contributions fit into the overall system.
The paper “\textit{What do software architects really do?}”\cite{SoftwareArchitectsReallyDo}
suggests that architectural work includes both an “inwards” and “outwards” focus,
and that there should be a balance between them.

After the first assignment we did interviews and created personas, which helped us understand user needs.
This matches the inwards focus from the paper.
We then had a meeting to plan a solution and started building a basic frontend and backend.
We also spent time defining data structures and setting up an API, which shows some focus on architecture design.

The paper suggests a 50:25:25 split between internal design work, getting input, and communicating the architecture outwards.
However, we likely did not achieve an ideal balance, especially in the short term.

One of the main challenges we experienced is what the paper describes as “firefighting”,
where immediate implementation issues take priority over long-term architectural considerations.
Some decisions (like simple data structures and API design) were made quickly to get a working prototype.
While this approach enabled rapid progress, it also increases the risk of technical debt
and may make future scaling or modifications more difficult.

Looking at the project over time, our focus has shifted.
In the beginning, most of the work was external,
since we needed input to understand the problem.
In later sprints, the focus has been more internal,
since we needed to implement functionality.
However, this also meant less continuous feedback from stakeholders,
which could lead to misalignment with user needs.

Overall, architectural concerns were considered throughout the project,
but not always addressed in a systematic or balanced way.
The lack of a clearly defined architectural role, combined with time constraints,
led to a stronger focus on implementation than long-term design.

This suggests that our process may partially resemble the “absent architect” antipattern,
where architectural responsibility is diffused and occasionally overshadowed by short-term priorities.

While the 50:25:25 distribution proposed in the paper is not a strict rule,
our experience indicates that a more deliberate allocation of architectural responsibilities
could improve decision-making, reduce technical debt, and support future system evolution.