\section{Ideal workflow design}


Designing an ideal software development process is inherently challenging,
as no single approach guarantees success across all projects.
Software teams vary in size, experience, technical complexity, and goals,
meaning that processes must be adapted to their specific context rather than adopted blindly.

This aligns with findings from the paper \textit{Catching up with Method and Process Practice} \cite{CatchingUpWithMethods},
which shows that software teams rarely follow a single methodology strictly.
Instead, they tend to combine practices from multiple approaches into hybrid processes.
The paper also highlights that teams often deviate from prescribed methods,
either intentionally or due to external constraints,
which can reduce the effectiveness of those practices if they are not consistently applied.

Our project experience reflected this in practice.
We combined Scrum practices such as sprint planning and backlog management
with XP practices like continuous integration and incremental development.
However, these practices were not always applied consistently.
For example, daily Scrum meetings were irregular,
and pair programming was only used in certain situations due to scheduling difficulties.

We also observed that simply combining practices is not sufficient.
The paper emphasizes that successful teams actively refine and adapt their process over time.
In our case, time constraints limited our ability to systematically improve how practices were integrated,
which likely reduced their effectiveness.

Overall, both the literature and our experience suggest that
a hybrid process is realistic, but its success depends on
how well practices are coordinated, adapted, and consistently applied.


\subsection{Coordinator Role}

In our project, we did not assign a clearly defined leadership role responsible for
coordinating tasks, tracking progress, and ensuring alignment across the team.
Instead, responsibility was shared among all members, which initially seemed flexible
and aligned with the collaborative nature of agile development.

However, this approach also introduced challenges.
Without a dedicated role overseeing task distribution and progress,
it became difficult to maintain a consistent overview of what had been completed,
what was in progress, and what remained.
This sometimes led to uneven workload distribution, duplicated efforts,
and delays when tasks depended on work from others.

From a Scrum perspective, this can be related to the absence of a clearly defined
\textit{Scrum Master} role.
In Scrum, the Scrum Master is responsible for facilitating the process,
removing obstacles, and ensuring that the team follows agreed practices.
While this role does not function as a traditional manager,
it plays an important part in maintaining structure and flow within the team.

In our case, some Scrum practices were applied informally,
but without a person explicitly responsible for maintaining them,
they were not always followed consistently.
For example, task tracking and coordination depended heavily on individual initiative,
rather than a shared and continuously maintained overview.

\subsection{Meetings}

One of the main challenges we encountered during our meetings was the lack of clear outcomes.
We often scheduled longer meetings (e.g., two hours) to discuss problems and make decisions.
While discussions were often productive,
they did not consistently result in clearly defined decisions or actionable outcomes.

In addition, there were periods of limited communication over time,
which resulted in decisions not being clearly communicated to all team members.
This created misunderstandings and inconsistencies in how tasks were carried out.

These issues highlight the importance of structured meetings,
clear decision-making processes, and proper documentation of outcomes.

\subsection{XP}

We applied several practices inspired by Extreme Programming (XP), including continuous integration,
incremental development, and occasional pair programming.
These practices contributed positively to development by enabling faster feedback
and improving collaboration between team members.

Continuous integration, in particular, helped detect errors early and reduced integration issues when merging code.
This aligns well with XP principles of frequent integration and rapid feedback.

However, XP practices were not applied consistently.
Pair programming was used only in certain situations, mainly due to scheduling difficulties.
Similarly, test-driven development (TDD) was not systematically followed,
as time constraints often led to writing tests after implementation rather than before.

This reflects a common challenge in adopting XP practices:
while they provide clear benefits,
they require consistent discipline and coordination to be effective in practice.

\subsection{Design Thinking}

Overall, we followed many of the principles of design-thinking quite closely, especially in the starting phase of the project.
We found the "\textit{introduction to design thinking}"\cite{DesignThinking} to give some good ideas on how to go about handling
the non-trivial task to design software for other users than yourself, in a domain you have limited knowledge about.
We really tried to understand the intent (the "why's") behind the responses we got in the interview.
And when we were trying to condense the insights gathered from interviews, we found it useful with open-minded brainstorming.

The review article "\textit{Design Thinking was supposed to fix the world...}"\cite{fix_the_world}
brings up a lot of valid criticism towards Design Thinking, but a lot of the focus on the article is
about issues in how Design Thinking has been marketed, and how it over-promises on fixing problems that are admittedly hard.
Certain organizations (IDEO is brought up in the review) makes money on selling Design Thinking as a miracle cure, allowing designers
to quickly become experts in any field, while the practices it highlights are really quite basic.
Empathizing, Brainstorming and Prototyping are not novel ideas, and are used plentifully in other scenarios, and was not invented by these organizations who popularized and packaged them.

We don't hold the design thinking process in such a negative view as can be interpreted from the article, but we believe this is due to how design thinking was presented to us.
We were not "sold" design thinking as something that would solve all our problems, but rather an initial framework on how to start working in a software development process.
The article does not mainly criticize the general practices, but rather misuse of these practices, and limitations in the approach when applied to large and complex systems.
Of course, no one would disagree that empathizing or prototyping and feedback is good, but although trivial, for beginner developers such as us, a framework like this is a useful guiding structure.

The criticism of the paper towards how design thinking has been marketed and misused, are not problems we have that much insight to,
as we are still beginner developers and have not seen many such examples in practice.
We used prototyping as a practical way to deliver something that could provide feedback and work as proof of concept for ourselves, our stakeholders,
and as a deliverable for the project, not simply for the sake of prototyping.
Although we mainly focused on a single prototype rather than continuously providing smaller iterations, contrasting the approach in the framework slightly.

Similarly for gathering stakeholder insights, we did not superficially empathize, nor did we claim to be experts afterwards.
Rather we used the framework as pointers to how to go about interviewing, since none of us had particular experience with that from before.

We also found that design thinking did not really help us with what we struggled with most, which was time constraints.
Had we been more diligent with following the framework (such as making cardboard prototypes or pausing development to get feedback on individual features)
or had been forced to repeat the process each sprint, it would likely worsen this problem as well.
Iteration and validation requires time, and we can not necessarily assume we have time to spare.

\subsection{Our Ideal Workflow}

Based on these challenges, we propose an improved workflow that builds on our experience.
If the project were to be conducted again,
we would adopt a hybrid development process combining elements of Scrum, Kanban, and XP,
with the goal of balancing flexibility and structure.

First, we would introduce a clearly defined coordinating role,
similar to a Scrum Master.
This role would act as a facilitator responsible for:
\begin{itemize}
    \item maintaining an overview of tasks and progress
    \item ensuring balanced workload distribution
    \item facilitating communication and coordination
    \item identifying and resolving blockers early
\end{itemize}

Second, we would use shorter iterations, such as weekly planning cycles,
instead of longer sprint periods.
This would allow the team to adapt more easily to changing schedules
and maintain steady progress.

Third, we would introduce structured meetings.
Short stand-up meetings would be held at least twice per week,
with a clear focus on progress, blockers, and next steps.
All meetings would have predefined agendas and result in documented decisions.

From XP, we would retain practices that improve code quality.
All code changes should be submitted through pull requests
and reviewed by at least one team member.
Continuous integration should remain in place to detect issues early.
Practices such as pair programming and TDD would be applied selectively,
focusing on complex or critical parts of the system.

Design thinking would be used as a flexible tool rather than a strict process,
supporting idea generation and stakeholder understanding when appropriate.

\subsection{Evaluation of the Proposed Workflow}

To evaluate whether the improved workflow is effective,
both quantitative and qualitative measures should be used.

Quantitative measures include:
\begin{itemize}
    \item number of completed tasks per iteration
    \item frequency of merge conflicts
    \item adherence to planned deadlines
    \item meeting participation rates
\end{itemize}

Qualitative measures include:
\begin{itemize}
    \item perceived communication quality
    \item workload balance
    \item stress level
    \item confidence in project progress
\end{itemize}

Regular retrospective meetings would allow the team to reflect on these factors
and continuously adjust the process.

\subsection{Conclusion}

The ideal workflow for this project is not a strict implementation of a single methodology,
but a hybrid approach adapted to the realities of a student development team.
By combining structured coordination, lightweight communication,
and selected engineering practices,
the team is more likely to achieve better alignment, improved code quality,
and a more efficient and predictable development process.

