\section{Requirements}

\subsection{Overview}
Based on the pre-study, a set of functional and non-functional requirements were derived
to address the challenges related to motivation, engagement, and learning.

\subsection{Functional Requirements}
\begin{itemize}
    \item Students should be able to track their progress without relying solely on grades
    \item Students should be able to ask anonymous questions
    \item Students should be able to participate in study groups
    \item The system should provide feedback on participation
    \item The system should support gamification elements such as streaks and XP
\end{itemize}

\subsection{Non-functional Requirements}
\begin{itemize}
    \item Usability: The system must be intuitive and easy to use
    \item Accessibility: The system should work on common devices
    \item Scalability: The system should support many users
    \item Maintainability: The system should be modular and extensible
\end{itemize}

\subsection{Traceability to Personas}
The requirements are derived from user needs identified in the personas.
For example, Fiona requires independent learning support, while Elias requires structure and guidance.

\subsection{Sustainability Considerations}
At this stage of the project, sustainability considerations are necessarily limited, as no concrete solution has yet been defined. 
Nevertheless, several relevant aspects have been identified.

From a technical perspective, the solution must align with users’ existing knowledge and access to technology, 
such as personal computers and mobile devices. 
This implies that any future system should be easy to use and accessible within realistic technical constraints.

From a social perspective, the project focuses on improving motivation, engagement, and encouragement within educational contexts. 
Addressing these issues has the potential to positively impact users’ well being and overall learning experience.

Regarding economic sustainability, no budget has been defined at this stage. 
The project will explore possibilities for making the solution freely available. 
No physical production is planned.

Environmental considerations include limiting or avoiding excessive use of resource intensive AI technologies, as high computational usage may have negative environmental impacts.
%TODO maybe compine thess sections, add artifacts
\subsection{Sustainability Assessment and Artefacts}

To evaluate the broader impact of our system, we applied principles from the sustainability
assessment framework presented in \cite{SAF-Toolkit}.
This framework emphasizes analyzing software systems across multiple dimensions,
including technical, environmental, economic, and social aspects.

As a result, several artefacts were developed.
First, a systemic impact map was created to visualize how the system influences different factors,
such as social interaction, server load, and energy consumption.
This helped identify both positive and negative consequences of the system in a broader context.

Second, a set of quality attributes was defined, linking system features to sustainability dimensions and measurable indicators.
This provided a structured way to evaluate trade-offs, for example between increased functionality and resource usage.

Finally, key performance indicators (KPIs) were established to measure success in areas such as student motivation,
social interaction, and economic sustainability.
These KPIs make it possible to assess whether the system meets its intended goals over time.

Together, these artefacts support a more holistic understanding of the system’s impact and guide future design decisions toward more sustainable outcomes.
%TODO: Add figure of canvas board from disc.